Multi-modality Imagery Database for Plant Phenotyping

### 2015-04-28 datapaper_intro.tex
xm's first edits

Plant visual phenotyping aims to analyze and categorize the visual appearance of plants~\cite{}. In old days, this was conducted via manual visual observation~\cite{Erblichkeit1903}. Today, with the increasing lower cost of imaging sensors and advances of computer vision technologies, image-based automatic plant visual phenotyping is growing into a desirable and viable solution~\cite{cruz2015depi}. In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the goal of raising testable biological hypotheses to solve the aforementioned problems.

Due to diverse variations of leaf appearance, layout, growth and movement, plant image analysis is a non-trivial computer vision task~\cite{}. In order to develop advanced algorithms, image databases that are well representative of this application domain is highly important. In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000}, LFW~\cite{LFW}, Caltech$101$~\cite{Fei-Fei2004}). However, the publicly available database for plant phenotyping is still limited, with the only exception of LSC database \cite{scharr2014annotated}, which, nevertheless, has its own limitations on the type of images (RGB only), and is only suitable for a small set of applications.

To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database, termed ``MSU-PID''. The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of sensors, i.e. Fluorescence, IR, RGB color, and depth.
%
All four sensors are synchronized and are programmed to periodically capture data for multiple days. Checkerboard-based camera calibration is perform between the multiple sensors, which results in the explicit correspondence between the pixels of any two modalities. For a subset of the database, we manually label the ground truth on the leaf identification number, leaf tip locations and leaf segments. To provide a performance baseline for future comparison, we apply our automatic leaf segmentation approach~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the challenge of image analysis on this database.

In summary, this paper and our database have made the following main contributions.
\begin{itemize}
\item MSU-PID is the first {\it multi-modality} plant image database. This allows researchers to study the strength and weakness of individual modality, as well as their fusion in plant image analysis.
\item Our imaging setup and the variety of manual label make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis tasks, including leaf segmentation, leaf counting, leaf alignment, leaf tracking, leaf growth prediction.
\end{itemize}

>>>>

The objective of {\it plant visual phenotyping} is to analyze and categorize the visual appearance of plants. %~\cite{}. 
In old days, plant phenotyping was conducted through manual visual observation~\cite{Erblichkeit1903}. 
Today, motivated by the increasing lower cost of imaging sensors and advances of computer vision technologies, image-based automatic plant visual phenotyping is quickly growing into a desirable and viable solution~\cite{cruz2015depi}. 
In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve the aforementioned problems.

\begin{table*}[t!]
	\centering
	\caption{Plant image databases, where the abbreviation in ``Applications'' column is defined as Leaf Classification (LC), Leaf Segmentation (LS), Leaf Counting (LO), Leaf Alignment (LA), and Leaf Tracking (LT).}
	%\resizebox{12cm}{!} {
	%\begin{tabular}{|l@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}
	\begin{tabular}{l|c|c|c|c|c|c}
		\hline
		\multirow{2}{*}{Database}&  \multirow{2}{*}{Modality}  & Appli-& Plant & Subject/ &Total  &  Labeled   \\ 						
			&         & cations &            Type         &       Classe \#         &  Image \#    & Image \# \\ \hline

Swedish leaf &  Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
Flavia& RGB  & LC& Leaves & $32$  & $2,120$ & $2,120$ \\ \hline
Leafsnap  & RGB & LC& USA trees & $184$ & $29,107$  &  $29,107$ \\ \hline
Crop/weed &  RGB &Weed det. & Crop/weed & $2$  & $60$ & $60$ \\ \hline
\multirow{2}{*}{LSC} & \multirow{2}{*}{RGB}  & \multirow{2}{*}{LS, LO} & Arabidopsis &  $43$ & $6287$ & $201$ \\ \cline{4-7}
							    &  & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
\multirow{2}{*}{MSU-PID}  & Fluorescence,  & LS, LO, & Arabidopsis &  $20$ & $XXX$ & $XXX$ \\ \cline{4-7}
							    & IR, RGB, Depth & LA, LT & Bean & $5$ & $XXX$ & $XXX$ \\ \hline
	       \hline
	\end{tabular}
	%}
	\label{tab:database}
\end{table*}

Due to diverse variations of leaf shape, appearance, layout, growth and movement, plant image analysis is a non-trivial computer vision task~\cite{Minervini2015}. 
In order to develop advanced computer vision algorithms, image databases that are well representative of this application domain is highly important. 
In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000} and LFW~\cite{LFW}). 
However, the publicly available database for plant phenotyping is still very limited, with the only exception of LSC database~\cite{scharr2014annotated}, which, nevertheless, has its own limitations on the type of images (RGB only) and is only suitable for a small set of plant image analysis applications.

To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database at Michigan State University (MSU), termed ``MSU-PID''. The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of sensors, i.e., Fluorescence, infrared (IR), RGB color, and depth.
All four sensors are synchronized and are programmed to periodically capture data for multiple consecutive days. Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities. 
For a subset of the database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips and leaf segments. 
To provide a performance baseline for future research and comparison, we apply our automatic leaf segmentation framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the unique challenge of image analysis on this database.

In summary, this paper and our database have made the following main contributions.
\begin{itemize}
\item MSU-PID is the first {\it multi-modality} plant image database. This allows researchers to study the strength and weakness of individual modality, as well as their various combinations in plant image analysis.
\item Our imaging setup and the variety of manual labels make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis applications, including leaf segmentation, leaf counting, leaf alignment, leaf tracking, and leaf growth prediction.
\end{itemize}

### 2015-04-28 datapaper_prior.tex
xi_doublecolumn
xm's first edits

Databases drive computer vision research. Hence, it is always important to develop and promote properly captured databases in the vision community. While there is a clear desire to apply computer vision to plant imagery, the lack of databases is an obstacle for the further study and development.

We summarize all existing publicly available databases that are related to plant imagery in Table~\ref{tab:database}. In terms of potential applications of the databases, they can be categorized into two types. The first type is for the general purpose of recognizing a particular species of tree or plant. The Swedish leaf database~\cite{soderkvist2001computer} is probably the first leaf database even though the images are captured by scanners. The Flavia database~\cite{wu2007leaf} is considerably larger and a neural network is used to train a leaf classifier. The most recent leafsnap project is an impressive effort that includes a very large dataset of $184$ tree types~\cite{kumar2012leafsnap}. A mobile phone application is also developed to make the leaf classification system portable. Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the field, and used for classifying crop vs.~weed. Note that in this type of databases, normally only a single leaf is imaged and as a result, the challenging problem of leaf segmentation has been bypassed.

The second type of databases is for plant phenotyping, where it is important to capture plant images without interfering the growth of plants. Thus, non-destructive approaches are taken and the entire plant is imaged. The LSC database~\cite{scharr2014annotated} is the most similar one to our database. It captures a large set of RGB images for the Arabidopsis and Tobacco plants. The provided manual labels allow the evaluation of leaf segmentation and leaf counting. In comparison, our MSU-PID database utilizes four sensing modalities in the data capturing, each providing different aspects of plant appearance.
Our manual label also enable us to develop algorithm on additional applications such as leaf tracking and alignment.

\begin{table}[t!]
	\centering
	\caption{Plant image databases, where the abbreviation in ``Applications'' column is defined as Leaf Classification (LC), Leaf Segmentation (LS), Leaf Counting (LO), Leaf Alignment (LA), and Leaf Tracking (LT).}
	\resizebox{12cm}{!} {
	%\begin{tabular}{|l@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|}
	\begin{tabular}{l|c|c|c|c|c|c}
		\hline
		\multirow{2}{*}{Database}&  \multirow{2}{*}{Modality}  & Appli-& Plant & Subject/ &Total  &  Labeled   \\ 						
			&         & cations &            Type         &       Classe \#         &  Image \#    & Image \# \\ \hline

Swedish leaf &  Scaned leaf & LC& Swedish trees & $15$ & $1,125$ & $1,125$ \\ \hline
Flavia& RGB  & LC& Leaves & $32$  & $2,120$ & $2,120$ \\ \hline
Leafsnap  & RGB & LC& USA trees & $184$ & $29,107$  &  $29,107$ \\ \hline
Crop/weed &  RGB &Weed det. & Crop/Weed & $2$  & $60$ & $60$ \\ \hline
\multirow{2}{*}{LSC} & \multirow{2}{*}{RGB}  & \multirow{2}{*}{LS, LO} & Arabidopsis &  $43$ & $6287$ & $201$ \\ \cline{4-7}
							    &  & & Tobacco & $80$ & $165,120$ & $83$ \\ \hline
\multirow{2}{*}{MSU-PID}  & Fluorescence,  & LS, LO, & Arabidopsis &  $20$ & $XXX$ & $XXX$ \\ \cline{4-7}
							    & IR, RGB, Depth & LA, LT & Bean & $5$ & $XXX$ & $XXX$ \\ \hline
	       \hline
	\end{tabular}
	}
	\label{tab:database}
\end{table}

>>>>

Databases drive computer vision research. 
Hence, it is always important to develop and promote properly captured databases in the vision community. 
While there is a clear desire to apply computer vision to plant image analysis, the lack of publicly available plant image databases has been an obstacle for the further study and development.

We summarize all existing publicly available databases that are related to plant imagery in Table~\ref{tab:database}. In terms of potential applications of these databases, they can be categorized into two types. 
The first type is for the general purpose of recognizing a particular species of tree or plant. 
The Swedish leaf database~\cite{soderkvist2001computer} is probably the first leaf database even though the images are captured by scanners. 
The Flavia database~\cite{wu2007leaf} is considerably larger and a neural network is utilized to train a leaf classifier. 
The most recent leafsnap project is an impressive effort that includes a very large dataset of leaves for $184$ tree types~\cite{kumar2012leafsnap}. 
A mobile phone application is also developed to make the leaf classification system portable. Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the real field, and used for the classification of crop vs.~weed. 
Note that in this type of databases, normally only a {\it single} leaf is imaged in a relatively constrained imaging environment and as a result, the challenging problem of leaf segmentation has been bypassed.

The second type of databases is for plant phenotyping, where it is important to capture plant images without interfering the growth of plants. 
Thus, non-destructive imaging approaches are taken and the entire plant is imaged. The LSC database~\cite{scharr2014annotated} is the most relevant one to our database. It captures a large set of RGB images for the Arabidopsis and Tobacco plants. The provided manual labels allow the evaluation of leaf segmentation and leaf counting. In comparison, our MSU-PID database utilizes four sensing modalities in the data capturing, each providing different aspects of plant visual appearance.
Our diverse manual labels also enable us to develop algorithms for additional applications such as leaf tracking and leaf alignment.
